Hierarchical Time Series Forecasting in Emergency Medical Services

### 2023-07-18 manuscript/05-results.qmd
ensemble 2 removed from table 3

msse1 <- rmsse |>
  filter(
    method %in% c("mint", "base"),
    model != "qcomb",
    h > 42
  ) |>
  mutate(model = factor(model,
    levels = c("naiveecdf","ets","iglm","tscount","ensemble","ensemble2"),
    labels = c("Naive", "ETS", "GLM", "TSGLM","Ensemble","Ensemble2")),
    method = factor(method, levels = c("base", "mint"), labels = c("Base", "MinT")),
  ) |>
  group_by(method, model, series) |>
  summarise(msse = mean(msse), .groups = "drop") |>
  pivot_wider(names_from = series, values_from = msse) |>
  select(Method = method, Model = model, Total, `Control areas`, `Health boards`, Bottom) |>
  set_to_bold()
mase1 <- mase |>
  filter(
    method %in% c("mint", "base"),
    model != "qcomb",
    h > 42
  ) |>
  mutate(
    model = factor(model,
      levels = c("naiveecdf","ets","iglm","tscount","ensemble","ensemble2"),
      labels = c("Naive", "ETS", "GLM", "TSGLM","Ensemble","Ensemble2")),
    method = factor(method, levels = c("base", "mint"), labels = c("Base", "MinT"))
  ) |>
  group_by(method, model, series) |>
  summarise(mase = mean(mase), .groups = "drop") |>
  pivot_wider(names_from = series, values_from = mase) |>
  select(Method = method, Model = model, Total, `Control areas`, `Health boards`, Bottom) |>
  set_to_bold()
crps1 <- readr::read_rds(here::here("results/crps.rds")) |>
  filter(method %in% c("mint", "base"),
         model != "qcomb",
         h > 42
  ) |>
  mutate(model = factor(model,
    levels = c("naiveecdf","ets","iglm","tscount","ensemble","ensemble2"),
    labels = c("Naive", "ETS", "GLM", "TSGLM","Ensemble","Ensemble2")),
    method = factor(method, levels = c("base", "mint"), labels = c("Base", "MinT"))
  ) |>
  group_by(method, model, series) |>
  summarise(crps = mean(crps), .groups = "drop") |>
  pivot_wider(names_from = series, values_from = crps) |>
  select(Method = method, Model = model, Total, `Control areas`, `Health boards`, Bottom) |>
  set_to_bold()

>>>>

msse1 <- rmsse |>
  filter(
    method %in% c("mint", "base"),
    model != "qcomb",
    h > 42,
    model != "ensemble2"
  ) |>
  mutate(model = factor(model,
    levels = c("naiveecdf","ets","iglm","tscount","ensemble","ensemble2"),
    labels = c("Naive", "ETS", "GLM", "TSGLM","Ensemble","Ensemble2")),
    method = factor(method, levels = c("base", "mint"), labels = c("Base", "MinT")),
  ) |>
  group_by(method, model, series) |>
  summarise(msse = mean(msse), .groups = "drop") |>
  pivot_wider(names_from = series, values_from = msse) |>
  select(Method = method, Model = model, Total, `Control areas`, `Health boards`, Bottom) |>
  set_to_bold()
mase1 <- mase |>
  filter(
    method %in% c("mint", "base"),
    model != "qcomb",
    h > 42,
    model != "ensemble2"
  ) |>
  mutate(
    model = factor(model,
      levels = c("naiveecdf","ets","iglm","tscount","ensemble","ensemble2"),
      labels = c("Naive", "ETS", "GLM", "TSGLM","Ensemble","Ensemble2")),
    method = factor(method, levels = c("base", "mint"), labels = c("Base", "MinT"))
  ) |>
  group_by(method, model, series) |>
  summarise(mase = mean(mase), .groups = "drop") |>
  pivot_wider(names_from = series, values_from = mase) |>
  select(Method = method, Model = model, Total, `Control areas`, `Health boards`, Bottom) |>
  set_to_bold()
crps1 <- readr::read_rds(here::here("results/crps.rds")) |>
  filter(method %in% c("mint", "base"),
         model != "qcomb",
         h > 42,
         model != "ensemble2"
  ) |>
  mutate(model = factor(model,
    levels = c("naiveecdf","ets","iglm","tscount","ensemble","ensemble2"),
    labels = c("Naive", "ETS", "GLM", "TSGLM","Ensemble","Ensemble2")),
    method = factor(method, levels = c("base", "mint"), labels = c("Base", "MinT"))
  ) |>
  group_by(method, model, series) |>
  summarise(crps = mean(crps), .groups = "drop") |>
  pivot_wider(names_from = series, values_from = crps) |>
  select(Method = method, Model = model, Total, `Control areas`, `Health boards`, Bottom) |>
  set_to_bold()
